Verifying Demonstrations

### 2019-02-15 paper/adversary-model.tex
Changes to global, passive adversary

We now provide a concretely defined system and adversary model.
We give three definitions, each defining an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

@@

\item\label{deanonymizing-storage-adversary}
  \emph{National eavesdropping adversary}:
  The situation is the same as in \cref{in-system-adversary}, but now the storage 
  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
  However, \(W\) still learns only the protocol data, no auxiliary data.

@@

As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
such as Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
so the adversary cannot control \(S\), but since \(S\) provides public access 
the adversary can (possibly constantly) query it and learn things with little 
delay.
Note that the adversary is also allowed to submit data to \(S\) for storage, 
just like everyone else.

\Cref{deanonymizing-storage-adversary} is a stronger adversary.
Although the adversary cannot observe the channel between \(P\) and \(S\), the 
adversary can still learn the identity of \(P\).
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
the identity of \(P\) in the communication with \(S\).

>>>>

We now provide a concretely defined system and adversary model.
We give three definitions, each defines an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

@@

\item\label{deanonymizing-storage-adversary}
  \emph{Global, passive adversary}:
  The situation is the same as in \cref{in-system-adversary}, but now the storage 
  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
  However, \(W\) still learns only the protocol data, no auxiliary data.

@@

As to \(S\), \cref{in-system-adversary} is equivalent to the adversarial 
storage \(S\) receiving only perfectly anonymous connections.
Another way to see it is that the adversary cannot control \(S\) but can learn 
what \(S\) learns as soon as \(S\) learns it; \eg \(S\) is operated outside the 
adversary's jurisdiction and so the adversary cannot control \(S\), but since 
\(S\) provides public access the adversary can (possibly constantly) query it 
and learn things with little delay.
Posed like this, the adversary cannot observe the channel between \(P\) and 
\(S\), \eg when \(P\) uses tools such as Tor~\cite{Tor}.
Note that the adversary is also allowed to submit data to \(S\) for storage, 
just like everyone else.

\Cref{deanonymizing-storage-adversary} is a much stronger adversary.
Even if the adversary cannot observe the channel between \(P\) and \(S\) (as is 
the case with Tor), the adversary can still learn the identity of \(P\) through 
\eg time-correlation attacks (as is the case with Tor).
A nation state can potentially monitor the traffic of all \acp{ISP} and thus 
perform time-correlation attacks on messages on the network and events observed 
from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
the identity of \(P\) in the communication with \(S\).
